---
title: "Homework 02"
format: 
  html: 
    embed-resources: true
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

Date: 2026-02-03
Data: Edible Plants Database
Source: GROW Observatory

# Research Question:
What is the relationship between optimal plant germination temperature and optimal plant growing temperature, and how does this vary by required sunlight?

```{r}
# Reading in the Data + loading packages
library(tidyverse)

edible_plants <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-02-03/edible_plants.csv')

edible_plants <- edible_plants |> 
  filter(temperature_germination != is.na(temperature_germination)) |> 
  filter(temperature_growing != is.na(temperature_growing))
```

```{r}
# Creating a visualization
edible_plants |> 
  ggplot(aes(x = water, fill = sunlight)) +
  labs(x = "Required Water",
       title = "Required Water versus Required Sunlight",
       subtitle = "How much water plants require relative to how much sunlight they require.",
       fill = "Required Sunlight") +
  scale_fill_viridis_d() + 
  geom_bar()
```


