---
title: "Homework 06"
format: 
  html: 
    embed-resources: true
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

Date: 2026-03-24 \
Data: One Million Digits of Pi \
Source: Manasseh, #TidyTuesday Community \

# Research Question: \
What is the most common digit in the first 1000001 digits of pi?

```{r}
# Reading in the data + packages

library(ggplot2)
library(tidyverse)
pi_digits <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-03-24/pi_digits.csv')
```

```{r, fig.alt = "This bar graph shows how often digits show up in the first million digits of pi."}
# Visualizing the data

pi_digits |> 
  count(digit) |> 
  mutate(digit = as.factor(digit)) |> 
  ggplot(aes(x = digit, y = n/10000)) +
  geom_col() +
  geom_text(aes(label = n/10000), vjust = -0.5) +
  theme_minimal() +
  labs(caption = "Source: Multiple | TidyTuesday HW6 | Katherine Manuel",
       title = "The First Million Digits of Pi Do Not Appear Equally",
       x = "Pi Digits",
       y = "Number of Occurences (in ten-thousands)",
       subtitle = "Digits such as 6 and 1 appear less frequently, while digits 4 and 5 are more frequent.")
```

