---
title: "Homework 08"
format: 
  html: 
    embed-resources: true
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

```{r}
# reading in the data

beaufort_scale <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-04-14/beaufort_scale.csv')
birds <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-04-14/birds.csv')
sea_states <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-04-14/sea_states.csv')
ships <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-04-14/ships.csv')

```

```{r}
# loading packages

library(dplyr)
library(tidyverse)
library(ggplot2)
```

```{r}
# cleaning data for viz
new_birds <- birds |> 
  filter(!is.na(age)) |> 
  filter(!is.na(count)) |> 
  
  # removing ages from birds
  mutate(species_common_name = str_trim(str_remove(species_common_name, " [A-Z]+$"))) |> 
  mutate(species_common_name = str_trim(str_remove(species_common_name, "AD"))) |> 
  mutate(species_common_name = str_remove(species_common_name, " SUB")) |> 
  
  # removing all unidentified/dubiously-identified birds
  filter(!str_detect(species_common_name, "unidentified")) |> 
  filter(!str_detect(species_common_name, "/")) |> 
  
  # changing age order
  mutate(age = factor(age, levels = c("juvenile", "immature", "subadult", "adult")))
```

```{r, fig.alt = "This heat map shows how NZ bird grouping patterns by species and age."}
# viz
new_birds |> 
  ggplot(aes(x = age, y = species_common_name, fill = count)) +
  geom_tile() +
  scale_fill_viridis_c(trans = "log") +
  theme_minimal() +
  labs(title = "Most NZ Seabirds Move In Smaller Groups",
       caption = "Source: Te Papa Tongarewa, The Museum of New Zealand | TidyTuesday HW8 | Katherine Manuel",
       x = "Species",
       y = "Age Group",
       fill = "Average Number of Birds in Group")

```
