---
title: "Homework 07"
format: 
  html: 
    embed-resources: true
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

```{r}
# reading in the data

repairs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-04-07/repairs.csv')
repairs_text <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-04-07/repairs_text.csv')
```

```{r}
# loading packages

library(dplyr)
library(tidyverse)
library(ggplot2)
library(plotly)
library(countrycode)
```

```{r}
# cleaning data for viz

new_repairs <- repairs |> 
  filter(!is.na(estimated_year_of_production)) |> 
  filter(!is.na(repairability)) |> 
  filter(!is.na(repaired)) |> 
  filter(!is.na(country)) |> 
  filter(estimated_year_of_production > 1900) |> 
  filter(estimated_year_of_production < 2026)
```

```{r, fig.alt = "This interactive choropleth map show how repairability for products of different production years varies across countries."}
# creating the visualization

new_repairs |>
  group_by(country, estimated_year_of_production) |>
  summarize(repairability = mean(repairability, na.rm = TRUE), .groups = "drop") |>
  mutate(iso3_code = countrycode(country, origin = "iso2c", destination = "iso3c")) |>
  plot_ly(
    type = "choropleth",
    locations = ~iso3_code,
    locationmode = "ISO-3",
    z = ~repairability,
    frame = ~estimated_year_of_production,
    text = ~paste("Country:", country, "<br>Production Year:", estimated_year_of_production,
                  "<br>Repairability:", repairability),
    hoverinfo = "text",
    colorscale = "Viridis") |>
  layout(
    title = "Repairability by Country and Production Year",
    geo = list(showframe = FALSE, showcoastlines = TRUE),
    annotations = list(
      x = 1, y = -0.05,
      text = "Source: Repair Monitor | TidyTuesday HW7 | Katherine Manuel",
      showarrow = FALSE,
      xref = "paper", yref = "paper",
      xanchor = "right", yanchor = "auto"))
```

