---
title: "Homework 08"
format: 
  html: 
    embed-resources: true
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

```{r}
# reading in the data
financing_schemes <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-04-21/financing_schemes.csv')
health_spending <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-04-21/health_spending.csv')
spending_purpose <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-04-21/spending_purpose.csv')

```

```{r}
# loading packages

library(countrycode)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(plotly)
```

```{r, fig.alt = "This interactive choropleth map shows health spending by country per year, from 2016-2023."}
# cleaning data for visualization

spending_purpose <- spending_purpose |>
  mutate(continent = countrycode(country_name, origin = "country.name", destination = "continent"))

spending_purpose_map <- spending_purpose |>
  filter(str_detect(indicator_code, "_usd2023")) |> 
  filter(!is.na(continent)) |>
  group_by(iso3_code, country_name, continent, year) |>
  summarize(total_spending = sum(value, na.rm = TRUE), .groups = "drop")

plot_ly(
  spending_purpose_map,
  type = "choropleth",
  locations = ~iso3_code,
  locationmode = "ISO-2",
  z = ~total_spending,
  frame = ~year,
  text = ~paste("Country:", country_name, "<br>Year:", year, "<br>Spending:", round(total_spending, 2)),
  hoverinfo = "text",
  colorscale = "Viridis"
) |>
  layout(
    title = "Health Spending by Country per Year",
    geo = list(showframe = FALSE, showcoastlines = TRUE),
    annotations = list(
      x = 1, y = -0.05,
      text = "Source: WHO Global Health Expenditure Database (GHED) | TidyTuesday W13 | Katherine Manuel",
      showarrow = FALSE,
      xref = "paper", yref = "paper",
      xanchor = "right", yanchor = "auto")
  )
```

